\chapter{General remarks}
\label{ch:general_remarks}

%------------------------------------

\section{Notes on the assignment}
\label{sec:notes_on_ass}

None of the assignments for the Software Architectures course were submitted in the first examination period due to personal reasons.
Because of this, all of the code written for this assignment is written specifically for the second examination period.
One small \textit{bug} in the code was resolved after email communication with the teaching assistants.
This \textit{bug} and its solution will be explained later.
All other code was written by using the course material and the online Akka documentation\footnote{\url{https://akka.io/docs/}}.

%------------------------------------

\section{Important files}
\label{sec:important_files}

All code written is available on the GitHub repository for this assignment \citep{github_project}. 
Rights to this private GitHub repository can be granted upon request. 
A copy of this GitHub repository is accompanied by this report.
An overview of important files is given below:
\begin{itemize}
    \item \texttt{README.md}
    \begin{itemize}
        \item General information of the GitHub repository as well as the technical details about the used environment, running the project and validated output.
    \end{itemize}
    \item \texttt{assignment.pdf}, \texttt{Lennert-Bontinck-SA1.pdf} and \texttt{report/}
    \begin{itemize}
        \item The assignment PDF, this report and the source files of the report.
    \end{itemize}
    \item \texttt{code/Lennert-Bontinck-SA1/}
    \begin{itemize}
        \item The folder containing the code of the assignment solution.
        \item Instructions on how to run the code are available in the \texttt{README.md} file.
        \item \texttt{./src/main/resources/}: sub-folder containing the extracted input file and a shortened alternative. The results files are available under the sub-folder \texttt{./result/}.
        \item \texttt{./src/main/scala/Lennert\_Bontinck\_SA1/}: sub-folder containing the main Scala files. Multiple files are made for separate objects and classes. All code is well documented and discussed later in this report.
    \end{itemize}
\end{itemize}

